CUDA-accelerated genetic feedforward-ANN training for data mining

### 2010-07-09 doc/HPCS-proceedings-paper.tex
Formatted report to meet JPCS requirements
git-svn-id: http://svn.scesoc.ca/evolution/trunk@123 fee98b4c-d1c3-4d34-9525-a468159e4a48

% ===========================================================================
% Title:
% ---------------------------------------------------------------------------
% to create Type I fonts type "dvips -P cmz -t letter <filename>"
% ===========================================================================
\documentclass[11pt]{article}       %--- LATEX 2e base
\usepackage{latexsym}               %--- LATEX 2e base
%---------------- Wide format -----------------------------------------------
\textwidth=6in \textheight=9in \oddsidemargin=0.25in
\evensidemargin=0.25in \topmargin=-0.5in
%--------------- Algorithm --------------------------------------------------
\newtheorem{algX}{Algorithm}
\newenvironment{algorithm}       {\begin{algX}\begin{em}}%
                                 {\par\noindent --- End of Algorithm ---
                                 \end{em}\end{algX}}
\newcommand{\step}[2]            {\begin{list}{}
                                  {  \setlength{\topsep}{0cm}
                                     \setlength{\partopsep}{0cm}
                                     \setlength{\leftmargin}{0.8cm}
                                     \setlength{\labelwidth}{0.7cm}
                                     \setlength{\labelsep}{0.1cm}    }
                                  \item[#1]#2    \end{list}}
                                 % usage: \begin{algorithm} \label{xyz}
                                 %        ... \step{(1)}{...} ...
                                 %        \end{algorithm}
%--------------- Figures ----------------------------------------------------
\usepackage{graphicx}

@@

\title{CUDA-accelerated Genetic Feedforward-ANN Training for Data Mining}

% ############################################################################
% Author(s) (no blank lines !)
\author{
% ############################################################################
Catalin Patulea, Robert Peace, and James Green\\
School of Systems and Computer Engineering\\
Carleton University\\
Ottawa, Canada K1S 5B6\\
{\em cpatulea@sce.carleton.ca}, {\em rpeace@sce.carleton.ca}, {\em jrgreen@sce.carleton.ca}
% ############################################################################
} % end-authors
% ############################################################################

\maketitle

@@

In addition, parallelization methods of genetic algorithms involving multiple populations \cite{Alba1999} may interact favourably with data mining applications.  Seperate populations may be trained on different subsets of the training data, allowing for a more thorough search of the solution space which the training set presents.

% ############################################################################
% Bibliography
% ############################################################################
\bibliographystyle{unsrt}
\bibliography{bibliography}     %loads bibliography.bib

>>>>

% ===========================================================================
% Title:
% ---------------------------------------------------------------------------
% to create Type I fonts type "dvips -P cmz -t letter <filename>"
% ===========================================================================
\documentclass[letterpaper]{jpconf}       %--- LATEX 2e base
\usepackage{latexsym}               %--- LATEX 2e base
%---------------- Wide format -----------------------------------------------
\textwidth=6in \textheight=9in \oddsidemargin=0.25in
\evensidemargin=0.25in \topmargin=-0.5in
%--------------- Algorithm --------------------------------------------------
\newtheorem{algX}{Algorithm}
\newenvironment{algorithm}       {\begin{algX}\begin{em}}%
                                 {\par\noindent --- End of Algorithm ---
                                 \end{em}\end{algX}}
\newcommand{\step}[2]            {\begin{list}{}
                                  {  \setlength{\topsep}{0cm}
                                     \setlength{\partopsep}{0cm}
                                     \setlength{\leftmargin}{0.8cm}
                                     \setlength{\labelwidth}{0.7cm}
                                     \setlength{\labelsep}{0.1cm}    }
                                  \item[#1]#2    \end{list}}
                                 % usage: \begin{algorithm} \label{xyz}
                                 %        ... \step{(1)}{...} ...
                                 %        \end{algorithm}
%--------------- Figures ----------------------------------------------------
\usepackage{graphicx}

@@

\title{CUDA-accelerated genetic feedforward-ANN training for data mining}

% ############################################################################
% Author(s) (no blank lines !)
\author{Catalin Patulea, Robert Peace and James Green}
\address{School of Systems and Computer Engineering,
Carleton University,
Ottawa, Canada K1S 5B6}
\ead{cpatulea@sce.carleton.ca, rpeace@sce.carleton.ca, jrgreen@sce.carleton.ca}
% ############################################################################
% end-authors
% ############################################################################

@@

In addition, parallelization methods of genetic algorithms involving multiple populations \cite{Alba1999} may interact favourably with data mining applications.  Seperate populations may be trained on different subsets of the training data, allowing for a more thorough search of the solution space which the training set presents.\\

% ############################################################################
% Bibliography
% ############################################################################
\bibliographystyle{iopart-num}
\bibliography{bibliography}     %loads bibliography.bib
